### 2017-09-29 TF-vldb2018/sec-tsimAlg.tex

\revise{
We devise an algorithm \grouprec for \teamF, with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for strong simulation~\cite{MaCFHW14}.}

@@

\begin{example}
\label{exm-consistency}
\ni(1)  Consider pattern $P_2$ in Fig.~\ref{fig-consistency-example}.
One can verify that there exist no data graphs $G$ such that $P_2 \eeps G$ because (a) for any nodes $u$ in $G$, if $u$ matches with the node labeled with $B_2$, then it must match with the node labeled with $B_1$, and, hence, (b) the capacity upper bound on $B_1$ should not be less than the lower bound on $B_2$.

>>>>

\revise{
We devise an algorithm \grouprec for \teamF, with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for \warn{strong simulation}~\cite{MaCFHW14}.}

@@

\begin{example}
\label{exm-consistency}
\ni(1)  Consider pattern $P_2$ in Fig.~\ref{fig-consistency-example}.
One can verify that there exist no data graphs $G$ such that $P_2 \eeps G$ because (a) for any nodes $v$ in $G$, if $v$ matches with the node labeled with $B_2$, then it must match with the node labeled with $B_1$, and, hence, (b) the capacity upper bound on $B_1$ should not be less than the lower bound on $B_2$.
